### 2012-06-15 joint action and knowing others minds/submit philosophical studies  2012-01/second submit/reply to reviewer.txt

The reviewer's comments and two suggestions were extremely useful.  The paper has been  revised to incorporate both suggestions.

--- First suggestion:
"The authors might address what a passive observer C might think of what B is doing.  Suppose the passive observer knows what A is doing (trying to get the pram on the bus).  Then C, observing A's cues for engaging in joint activity with B, could infer as easily as B that A is trying to lift the stroller to help get it on the bus.  I don't think that this undermines the author's argument, because C relies on the very capacities to engage in interaction that the authors emphasize.  But it might be nice to address this sort of case, just to clarify their thesis:  after all, C does not on this occasion engage in any reciprocity, interaction, or willingness to interact.   (Nor does C rely on any deception or cognitive sophistication; cf. p14)."

--- Reply to first suggestion:
This has been done in a new section, section 8 on pp. 20-1 titled 'Observing Interaction'.  There is also a new paragraph on p. 15 (the third full paragraph) and corresponding minor changes to statements of the argument throughout.  As the reviewer points out, the suggestion doesn't undermine the main line of argument.  Even so, it seemed appropriate to devote a whole section to it both because it clarifies our thesis and because it suggests a further way in which interaction may matter for mindreading.

--- Second suggestion:
"Concerning the your-goal-is-my-goal inference: the authors rely on the idea that the mind-reader A has a fixed goal G so that when the other person B expresses willingness to engage in joint activity, A can infer that B will have the same goal.  But is this always the case?  Often when someone makes an overture to engage in shared activity, it's not always clear that you are supposed to keep on doing exactly what you were doing.  There are, of course, cases where someone joins in and adopts a goal that the other or others have.  But often shared activity gets individuals doing things they weren't doing before.  So when A signals that they are willing to act jointly, can the mindreader (B) assume that A has the same goal?  Couldn't A be trying to get him to have some different goal with him? So, clarifying the inference to rule out this case might be helpful."

--- Reply to first suggestion:
This has been done in with a slight change to premise (1) on page 13 and a new paragraph on page 14 (the second full paragraph) .

I've mentioned a couple of suggestions, but the paper is pretty much fit to be published as is.  I think it meets the high standards for Philosophical Studies.

### 2012-06-15 mindreading/conf espp 2012 symposium false belief counterfactuals perspective schurz rafetseder/false beliefs, perspectives and counterfactuals espp 2012 symposium submission.tex
minimal theory of mind sent to mind and language final (i hope)

\section{The puzzle}
Can we reject (\ref{infant_fb}), the claim that infants can represent false beliefs?  
This is what  Eva suggests in her paper.
But there is a growing body of evidence which appears to support  (\ref{infant_fb}).
From around their first birthday infants  predict actions of agents with false beliefs about the locations of objects \citep[]{en_1092, en_1208} and choose different ways of interacting with others depending on whether their beliefs are true or false \citep[]{en_1783,Knudsen:2011fk,southgate:2010fb}.  
And in much the way that irrelevant facts about the contents of others’ beliefs modulate adult subjects’ response times, such facts also affect how long 7-month-old infants look at some stimuli \citep[]{en_1821}.
The variety of paradigms measures---looking time, anticipatory looking, pointing and helping---makes it hard to dismiss these findings on methodological grounds.
And while some have proposed that infants might be tracking behaviour only \citet{en_1168, en_1169},
this proposal faces several objections \citep[e.g.][]{Song:2008qo}.
The core issue is not whether hypothetical behavioural strategies might in principle explain theory of mind abilities; it is whether all of these subjects’ actual behaviour reading capacities are flexible enough to explain the full range of their theory of mind abilities \citep[]{Apperly:2009ju}
In my view this is unlikely.
So straightforward rejection of  (\ref{infant_fb}) is not an option.

@@

A less obviously flawed approach to rejecting (\ref{fb_is_perspectives}) involves analysing particular false belief tasks.
Two explore this idea it will be useful to distinguish between two types of false belief task, call them Category A and Category B.
By stipulation Category A tasks have these features:
\begin{itemize}
\item Children tend to pass them some time after their third birthday.
\item Abilities to pass these tasks has a protracted developmental course stretching over months if not years.
\item Success on these tasks is correlated with developments in executive function \citep[]{en_410, en_1130} and language \citep[]{en_1209}.
\item Success on these tasks is facilitated by explicit training \citep[]{en_85} and environmental factors such as siblings \citep[]{en_507, en_1299}.  
\item Abilities to succeed on these tasks typically emerge from extensive participation in social interactions (as \citealp{en_1300} suggest).
\end{itemize}
All the other false belief tasks are in Category B.
It is these Category B tasks on which infants succeed.
The proposal we are considering (and which I shall reject) is this.  
\begin{quote}
	All Category A tasks impose a requirement (or set of requirements) other than the requirement to represent a false belief;
call this the \emph{Extraneous Requirement}.
	The connections between success on Category A tasks and processing perspective differences and counterfactual reasoning are a consequence just of the extraneous requirement.
\end{quote}
I am going to argue that this proposal should be rejected.
First note that the proposal is harder to defend than sometimes assumed.
For instance, philosophers sometimes mistakenly assume that all Category A tasks involve language or communication, whereas Category B tasks do not.
But some Category B tasks involve language and communication 
\citep{Knudsen:2011fk,Song:2008qo}
and there are non-verbal tasks in Category A
(\citealp{Call:1999co}; \citealp{low:2010_preschoolers} Study 2).
We should also note that children who fail Category A tasks can answer questions about perception or pretence that are word-for-word identical with the questions about false belief that they cannot answer correctly (\citealp{Gopnik:1994cb}; see also\citealp{Cluster:1996ht}).
So the Extraneous Requirement cannot be straightforwardly linked to language or communication.
There is a more general problem facing attempts to identify the Extraneous Requirement.
There is much variation among the tasks in Category A.
It is not just that some are verbal whereas others are nonverbal.
It is also that some involve prediction whereas others involve retrodiction or justification \citep[e.g.][]{Wimmer:1998kx},
some concern the first-person perspective, whereas others involve a second- or third-person perspective \citep[e.g.][]{Gopnik:1991db},
some involve interaction whereas in others the subject is a mere observer \citep[e.g.][]{Chandler:1989qa},
and some involve prediction actions whereas others involve predicting desires \citep{Astington:1991kk} or selecting an argument appropriate for someone with a false belief \citep{Bartsch:2000es}.
Despite all this variation and more, the Category A tasks all appear to measure a developmental transition \citep{Wellman:2001lz}.
This is a significant obstacle to identifying the Extraneous Requirement.
In fact, my view the currently available evidence supports the conclusion that there is no Extraneous Requirement.
And as far as I know the only plausible candidate for the transition  Category A tasks measure is a transition in the ability to represent beliefs.
This is why I don't think that we can straightforwardly reject  (\ref{fb_is_perspectives}).

>>>>

\section{The puzzle}
Can we reject (\ref{infant_fb}), the claim that infants can represent false beliefs?  
This is what  Eva suggests in her paper.
But there is a growing body of evidence which appears to support  (\ref{infant_fb}).
From around their first birthday infants  predict actions of agents with false beliefs about the locations of objects \citep[]{en_1092, en_1208} and choose different ways of interacting with others depending on whether their beliefs are true or false \citep[]{en_1783,Knudsen:2011fk,southgate:2010fb}.  
And in much the way that irrelevant facts about the contents of others’ beliefs modulate adult subjects’ response times, such facts also affect how long 7-month-old infants look at some stimuli \citep[]{en_1821}.
The variety of paradigms measures---looking time, anticipatory looking, pointing and helping---makes it hard to dismiss these findings on methodological grounds.
And while some have proposed that infants might be tracking behaviour only \citet{en_1168, en_1169},
this proposal faces several objections \citep[e.g.][]{Song:2008qo}.
The core issue is not whether hypothetical behavioural strategies might in principle explain theory of mind abilities; it is whether all of these subjects’ actual behaviour reading capacities are flexible enough to explain the full range of their theory of mind abilities \citep[]{Apperly:2009ju}.
In my view this is unlikely.
So straightforward rejection of  (\ref{infant_fb}) is not an option.

@@

A less obviously flawed approach to rejecting (\ref{fb_is_perspectives}) involves analysing particular false belief tasks.
Two explore this idea it will be useful to distinguish between two types of false belief task, call them Category A and Category B.
By stipulation Category A tasks have these features:
\begin{itemize}
\item Children tend to pass them some time after their third birthday.
\item Abilities to pass these tasks has a protracted developmental course stretching over months if not years.
\item Success on these tasks is correlated with developments in executive function \citep[]{en_410, en_1130} and language \citep[]{en_1209}.
\item Success on these tasks is facilitated by explicit training \citep[]{en_85} and environmental factors such as siblings \citep[]{en_507, en_1299}.  
\item Abilities to succeed on these tasks typically emerge from extensive participation in social interactions (as \citealp{en_1300} suggest).
\end{itemize}
All the other false belief tasks are in Category B.
It is these Category B tasks on which infants succeed.
The proposal we are considering (and which I shall reject) is this.  
\begin{quote}
	All Category A tasks impose a requirement (or set of requirements) other than the requirement to represent a false belief;
call this the \emph{Extraneous Requirement}.
	The connections between success on Category A tasks and processing perspective differences and counterfactual reasoning are a consequence just of the extraneous requirement.
\end{quote}
I am going to argue that this proposal should be rejected.
First note that the proposal is harder to defend than sometimes assumed.
For instance, philosophers sometimes mistakenly assume that all Category A tasks involve language or communication, whereas Category B tasks do not.
But some Category B tasks involve language and communication 
\citep{Knudsen:2011fk,Song:2008qo}
and there are non-verbal tasks in Category A
(\citealp{Call:1999co}; \citealp{low:2010_preschoolers} Study 2).
We should also note that children who fail Category A tasks can answer questions about perception or pretence that are word-for-word identical with the questions about false belief that they cannot answer correctly (\citealp{Gopnik:1994cb}; see also \citealp{Cluster:1996ht}).
So the Extraneous Requirement cannot be straightforwardly linked to language or communication.
There is a more general problem facing attempts to identify the Extraneous Requirement.
There is much variation among the tasks in Category A.
It is not just that some are verbal whereas others are nonverbal.
It is also that some involve prediction whereas others involve retrodiction or justification \citep[e.g.][]{Wimmer:1998kx},
some concern the first-person perspective, whereas others involve a second- or third-person perspective \citep[e.g.][]{Gopnik:1991db},
some involve interaction whereas in others the subject is a mere observer \citep[e.g.][]{Chandler:1989qa},
and some involve prediction actions whereas others involve predicting desires \citep{Astington:1991kk} or selecting an argument appropriate for someone with a false belief \citep{Bartsch:2000es}.
Despite all this variation and more, the Category A tasks all appear to measure a single developmental transition \citep{Wellman:2001lz}.
This is a significant obstacle to identifying the Extraneous Requirement.
In fact, my view the currently available evidence supports the conclusion that there is no Extraneous Requirement.
And as far as I know the only plausible candidate for the transition  Category A tasks measure is a transition in the ability to represent beliefs.
This is why I don't think that we can straightforwardly reject  (\ref{fb_is_perspectives}).
